Towards typed repositories of proofs \\[0.6em] \small \textsf{MIPS 2010}

### 2010-07-08 talks/MIPS2010/slides.tex
* Iteration.
git-svn-id: http://gasp.dev.regis-gianas.com/svn/trunk@145 403e655e-980a-47bd-8c60-1ee5348bb6b7
unicode -> math
git-svn-id: http://gasp.dev.regis-gianas.com/svn/trunk@146 403e655e-980a-47bd-8c60-1ee5348bb6b7

% Mode d'emploi: Switcher les deux lignes suivantes pour passer du
% mode présentation au handout
% ===================================================
\documentclass[ignorenonframetext,red]{beamer}
% \documentclass[12pt]{article} \usepackage{beamerarticle} \usepackage{fullpage}
% ===================================================

@@

First, we want to name all intermediate results, that is we don't want
to allow compound, deep applications. We remove general application
and make it a list of variables. Then, we need a new binder to
remember these flat applications. It will behave like a \textsf{let}
binding, and we add a corresponding entry to the environment. Note
that in terms, the type is not present whereas it is in the
environment.

@@

These simple modifications allow us to see this system as a typed
repository of proofs with a last modification: the usual judgement
becomes ``From repository Γ, term t of type u leads to repository
∆''. The analogy here is: Γ is the current database of versions, $t$
is a working directory with possible redundancies (it's not maximally
shared), and integration of $t$ into $\Gamma$ leads to $\Delta$, which
is maximally shared.

@@

\hrule
\begin{frame}{Typing rules}
  \begin{block}{Product - Init}
  \begin{mathpar}
    \large
    \infer                      % prod
    {\Gamma\vdash t : *\uncover<2->{ \Rightarrow \_} \and \Gamma[x:t]\vdash u :
      *\uncover<2->{\Rightarrow\Delta}}
    {\Gamma\vdash(x:t)\cdot u : *\uncover<2->{\Rightarrow\Delta}}
    \and
    \uncover<3->{               %init
      \infer{ }
      {\Gamma\vdash x : t \uncover<4->{\Rightarrow\Gamma}}
      \quad {\small [x:t]\in\Gamma}
    }
  \end{mathpar}
  \end{block}
\end{frame}
\hrule

@@

\hrule
\begin{frame}{Naming}

@@

>>>>

% Mode d'emploi: Switcher les deux lignes suivantes pour passer du
% mode présentation au handout
% ===================================================
%\documentclass[ignorenonframetext,red]{beamer}
\documentclass[12pt]{article} \usepackage{beamerarticle} \usepackage{fullpage}
% ===================================================

@@

First, we want to name all intermediate results, that is we don't want
to allow compound, deep applications. We remove general application
and make it a list of variables. Then, we need a new binder to
remember these flat applications and give a name to them. It will
behave like a \textsf{let} binding, and we add a corresponding entry
to the environment. Note that in terms, the type is not present
whereas it is in the environment.

@@

These simple modifications allow us to see this system as a typed
repository of proofs with a last modification: the usual judgement
becomes ``From repository $\Gamma$, term $t$ of type $u$ leads to
repository $\Delta$''. The analogy here is: $\Gamma$ is the current
database of versions, $t$ is a working directory with possible
redundancies (it's not maximally shared), and integration of $t$ into
$\Gamma$ leads to $\Delta$, which is maximally shared.

@@

\hrule
\begin{frame}{Typing rules}
  \begin{block}{Product - Init}
  \begin{mathpar}
    \large
    \infer                      % prod
    {\Gamma\vdash t : *\uncover<2->{ \Rightarrow \_} \and \Gamma[x:t]\vdash u :
      *\uncover<2->{\Rightarrow\Delta}}
    {\Gamma\vdash(x:t)\cdot u : *\uncover<2->{\textcolor{gray}{\Rightarrow\Delta}}}
    \and
    \uncover<3->{               %init
      \infer{ }
      {\Gamma\vdash x : t \uncover<4->{\Rightarrow\Gamma}}
      \quad {\small [x:t]\in\Gamma}
    }
  \end{mathpar}
  \end{block}
\end{frame}
\hrule

@@

\hrule
\begin{frame}{Content-aware names (implementation details)}

\begin{itemize}
\item Given ``$a$'', how to decide efficiently ``$[y = a : u] \in \Gamma$''?

\item Inspiration from \textsf{Git}~:
\begin{center}
\begin{math}
\begin{array}{lllr}
| \dots | &:& \kappa^\star \rightarrow \kappa & \text{Hash function}\\
\equiv    &:& \kappa \rightarrow \kappa \rightarrow \mathbb{B} & \text{Efficient comparison}\\
\nu       &:& \textsf{unit} \rightarrow \kappa & \text{Fresh key generator}
\end{array}
\end{math}
\end{center}
\end{itemize}

\begin{mathpar}
  \large
  \infer
      {\Gamma\vdash a : u \Rightarrow \_ \and \Gamma[|a|=a:u]\vdash t\{x/|a|\} :
        *\Rightarrow\Delta }
      {\Gamma\vdash (x=a)\cdot t : * \Rightarrow\Delta}
      \quad {\small [y=a:u] \notin\Gamma}
   \and
   \large
   \infer                      % prod
       {\Gamma\vdash t : *\uncover<2->{ \Rightarrow \_} \and \Gamma[k:t]\vdash u\{x/k\} :
         *\uncover<2->{\Rightarrow\Delta}}
       {\Gamma\vdash(x:t)\cdot u : * \textcolor{gray}{\Rightarrow\Delta}}
       \quad{\small k=\nu()}

\end{mathpar}

@@

\begin{itemize}
\item What if we reintroduce the lambda?
\begin{enumerate}
\item Constructive metatheory.
\item A language to express patches?
\end{enumerate}
\end{itemize}
\end{frame}
\hrule
